EpiExpert Crowd-Forecasting Performance Board

### 2021-02-11 evaluation/report-template.Rmd
switch to new leaderboard

locations <- c("Germany", "Poland")
forecast_dates <- as.character(unique(data$forecast_date[!is.na(data$forecast_date)]))
target_types <- c("case", "death")

@@

This table gives the rank of every forecaster among all forecasters for a given target and forecast date (1 is the best). Ranks are determined based on the weighted interval scores.

>>>>

locations <- c("Germany", "Poland")
forecast_dates <- rev(as.character(unique(data$forecast_date[!is.na(data$forecast_date)])))
target_types <- c("case", "death")

@@

This table shows (100 - the forecaster percentile rank) among all forecasters for a given target and forecast date. What happens is basically this: Every forecaster gets assigned a rank (1 is the best and the worst equals the number of available forecasts for that date). This rank is then transformed to a scale from 1 to 100 such that 100 is best and 0 is worst. Ranks are determined based on the weighted interval scores.

### 2021-02-11 evaluation/template-plot-forecasts.Rmd
switch to new leaderboard

```{r prediction-plots, echo = FALSE, results='asis', fig.width = 10, fig.height=20}

for (forecast_date in forecast_dates) {
  cat(paste0("\n\n## ", forecast_date), "{.tabset}\n\n")
  for (target_type in target_types) {
    cat("\n\n###", target_type, "\n\n")

    filter_both <- list(paste0("target_type %in% '", target_type, "'"))
    filter_truth <- list(paste0("target_end_date > '", as.Date(forecast_date) - 7 * 10, "'"), 
                         paste0("target_end_date <= '", as.Date(forecast_date) + 7 * 4, "'"))
    filter_forecasts <- list(paste0("forecast_date == '", as.Date(forecast_date), "'"))

    plot <- scoringutils::plot_predictions(data,
                                           x = "target_end_date",
                                           filter_both = filter_both,
                                           filter_truth = filter_truth,
                                           filter_forecasts = filter_forecasts,
                                           facet_wrap_or_grid = "grid",
                                           facet_formula = model ~ location_name,
                                           allow_truth_without_pred = FALSE,
                                           scales = "free") +
      ggplot2::ggtitle(paste0("Predictions for incident ", target_type,  "s")) + 
      ggplot2::theme(legend.position = "bottom")

    print(plot)
  }
}

>>>>

```{r prediction-plots, echo = FALSE, results='asis', fig.width = 10, fig.height=10}

for (forecast_date in forecast_dates) {
  cat(paste0("\n\n## ", forecast_date, "{.tabset} \n\n"))
  #, "{.tabset}\n\n")
  # plot_df <- dplyr::left_join(tidyr::expand(data = data, target_type, true_value, location_name, model), 
  #                             data)

  for (location in locations) {
    cat("\n\n###", location, "{.tabset} \n\n")

    for (target_type in target_types) {
      cat("\n\n####", target_type, "\n\n")

      filter_both <- list(paste0("target_type %in% '", target_type, "'"), 
                          paste0("location_name %in% '", location, "'"))
      filter_truth <- list(paste0("target_end_date > '", as.Date(forecast_date) - 7 * 10, "'"), 
                           paste0("target_end_date <= '", as.Date(forecast_date) + 7 * 4, "'"))
      filter_forecasts <- list(paste0("forecast_date == '", as.Date(forecast_date), "'"))

      plot <- scoringutils::plot_predictions(data,
                                             x = "target_end_date",
                                             filter_both = filter_both,
                                             filter_truth = filter_truth,
                                             filter_forecasts = filter_forecasts,
                                             facet_formula = ~ model,
                                             # facet_formula = model ~ target_type + location_name,
                                             # facet_wrap_or_grid = "facet",
                                             allow_truth_without_pred = FALSE,
                                             scales = "free") + 
        # ggplot2::ggtitle(paste0("Predictions for incident ", target_type,  "s")) + 
        ggplot2::theme(legend.position = "bottom", 
                       strip.placement = "outside")

      print(plot)
    }
  }
}

### 2021-02-11 evaluation/template-ranking-over-time.Rmd
switch to new leaderboard

```{r ranking-time, results = 'asis', fig.width=10, fig.height=9}
scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", 
                                                          "location_name", 
                                                          "target_type",
                                                          "forecast_date"), 
                                       compute_relative_skill = FALSE)

ranked_scores <- scores %>%
    dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
    dplyr::group_by(forecast_date, location_name, target_type) %>%
    dplyr::mutate(rank = rank(interval_score, ties.method = "average",
                              na.last = NA)) %>%
    dplyr::ungroup()

plot <- score_heatmap(ranked_scores, metric = "rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom")

>>>>

```{r ranking-time, results = 'asis', fig.width=12, fig.height=10}
scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", 
                                                          "location_name", 
                                                          "target_type",
                                                          "forecast_date"), 
                                       compute_relative_skill = FALSE)

ranked_scores <- scores %>%
  dplyr::mutate(forecast_date = as.Date(forecast_date)) %>%
  dplyr::group_by(forecast_date, location_name, target_type) %>%
  dplyr::mutate(num_forecasts = dplyr::n(), 
                unstandardised_rank = rank(interval_score, ties.method = "average",
                                           na.last = NA), 
                rank = round((1 - (unstandardised_rank - 1) / (num_forecasts - 1)) * 100)) %>%
  dplyr::ungroup()

plot <- score_heatmap(ranked_scores, metric = "rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom") +
    ggplot2::scale_fill_gradient(high = "white", low = "coral")
